 

### 2020-12-04 doc/manuscript/Dow_manuscript.Rmd
updated hypothesis table, knit in new tree-ring figure

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}

@@

```{r tree_rings, out.width="100%", echo=FALSE, fig.align="center", fig.cap= tree_rings_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/tree_rings.tif")
```

@@

## ("contributions beyond")
Our findings contribute to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (REFS), an earlier start to net C sequestration (REFS), and--as shown here--earlier initiation of stem growth (*CITE RELEVANT FIGS & TABLES* ).
Yet, an earlier start to the growing season does not imply a longer growing season [Table `r hypotheses`, Figs `r pheno_Tsensitivity`, `r DOYtiming`;  @zani_increased_2020].
Rather, growth finishes sooner-- presumably because of *C sink limitation* [@zani_increased_2020].

## ("science is better now")

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
## potential reviewers: Zani

@@

```{r tree_rings, out.width="100%", echo=FALSE, fig.align="center", fig.cap= tree_rings_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/tree_cores_tmax.png")
```

@@

## ("contributions beyond")
Our findings contribute to a broader picture of the influence of spring temperatures on forest ecosystem function. 
Warm spring temperatures result in earlier leaf-out (REFS), an earlier start to net C sequestration (REFS), and--as shown here--earlier initiation of stem growth (*CITE RELEVANT FIGS & TABLES* ).
Yet, an earlier start to the growing season does not imply a longer growing season [Table `r hypothesis_table`, Figs `r pheno_Tsensitivity`, `r DOYtiming`;  @zani_increased_2020].
Rather, growth finishes sooner-- presumably because of *C sink limitation* [@zani_increased_2020].
If sink limitation controls the end of woody growing season,

## ("science is better now")
As climate change accelerates and spring temperatures become increasingly warmer, growing seasons will start earlier, but this is unlikely to provide the increased carbon sequestration that is anticipated in most models [Table `r hypothesis_table`; Figs. `r pheno_Tsensitivity`, `r tree_rings`; @zani_increased_2020].
The implication is that temperate deciduous forests are likely to sequester less CO~2~ than most models suggest, implying that models are underestimating future atmospheric CO~2~ overall.

### 2020-12-04 doc/manuscript/tables_figures/tables.Rmd
updated hypothesis table, knit in new tree-ring figure

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2, " " )) %>%
  pack_rows("Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

#add footnote markers:
hypothesis_table[8,2] <- paste0(hypothesis_table[8,2], footnote_marker_number(1)) 
hypothesis_table[8,3] <- paste0(hypothesis_table[8,3], footnote_marker_number(2)) 
hypothesis_table[8,5] <- paste0(hypothesis_table[8,5], footnote_marker_number(3))

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2, " " )) %>%
  pack_rows("Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) %>%

#add footnote: 
kableExtra::footnote(number = c("One of nine species analyzed had significant positive response to April $T_{max}$; two had significant negative response to March $T_{max}$", "One of two species analyzed had signficant positive response to April $T_{max}$, both had negative response to May $T_{max}$", "The one species analyzed had a signficant negative response to April $T_{max}$."), footnote_as_chunk = FALSE, threeparttable=TRUE, escape = FALSE)
```
